### 2018-10-02 papers/journal/abstract.tex
added prelim and abstract

Vesicle Traffic Systems(VTSs) are the material transport 
mechanisms among the compartments inside the biological cells.
%
The compartments are viewed as nodes that are labeled with the
containing chemicals and the transport channels
are similarly viewed as labeled edges between the nodes.
%
Understanding VTSs is an ongoing area of research and for many cells
they are partially known.
%
For example, there may be undiscovered edges, nodes, or their labels
in a VTS of a cell.
%
It has been speculated that there are properties that the VTSs must
satisfy.
%
For example, stability, i.e., every chemical that is leaving a
compartment comes back.
%
Many synthesis questions may arise in this scenario, where we want
to complete a partially known VTS under a given property.
%
In the paper, we present novel encodings of the above questions
into the QBF(quantified Boolean formula) satisfiability problems.
%
We have implemented the encodings in a highly configurable tool
and apply to a couple of found-in-nature VTSs and 
several synthetic graphs.
%
Our results demonstrates that our method can scale upto the
graphs of interest.
%

>>>>

Vesicle Traffic Systems (VTSs) are the material transport 
mechanisms among the compartments inside the biological cells.
%
The compartments are viewed as nodes that are labeled with the
containing chemicals and the transport channels
are similarly viewed as labeled edges between the nodes.
%
Understanding VTSs is an ongoing area of research and for many cells
they are partially known.
%
For example, there may be undiscovered edges, nodes, or their labels
in a VTS of a cell.
%
It has been speculated that there are properties that the VTSs must
satisfy.
%
For example, stability, i.e., every chemical that is leaving a
compartment comes back.
%
Many synthesis questions may arise in this scenario, where we want
to complete a partially known VTS under a given property.
%
In the paper, we present novel encodings of the above questions
into the QBF (quantified Boolean formula) satisfiability problems.
%
We have implemented the encodings in a highly configurable tool
and applied to a couple of found-in-nature VTSs and 
several synthetic graphs.
%
Our results demonstrate that our method can scale up to the graphs of interest.

% Vesicle Traffic Systems(VTSs) are the material transport 
% mechanisms among the compartments inside the biological cells.
